---
title: "ModelBuilder"
author: "Naren Vijayakumar"
date: "Jan 14, 2017"
output: ioslides_presentation
---
<style type="text/css">
pre{
  font-size: 15px;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

* ***ModelBuilder*** is an easy to use and interactive linear model builder 
* Enables one to see the effects of different predictors on the ouput. 
* Once a model is built. It provides 
    + Summary of the model 
    + "Actual vs Predicted" Plot
* Application is hosted at <https://narenv.shinyapps.io/ModelBuilder/>

## Walkthrough
Select a Dataset, Choose Ouput and Predictors and Click Build
```{r fig.width=5, fig.height=5,echo=FALSE}
library(png)
library(grid)
img <- readPNG("images/Screenshot1.png")
 grid.raster(img)
```

## Output: "Actual vs Predicted" Plot

```{r echo=FALSE,message=FALSE}
library(plotly)
mymodel <- lm(mpg~cyl+disp+wt+am+gear,mtcars)
predicted_values <- predict(mymodel)
g <- ggplot(data.frame(Actual=mtcars$mpg,Predicted=predicted_values), 
            aes(x=Actual,y=Predicted)) + geom_point(color="blue")
ggplotly(g)

```

## Output: Model Summary
```{r fig.width=7, fig.height=4,echo=FALSE, fig.align='center'}
img <- readPNG("images/Screenshot2.png")
 grid.raster(img)
```




